---
title: "Lab 05 - Importing and Recoding `earthquakes`"
author: "Caroline Campbell"
date: "April 14, 2024"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
library(openintro)
library(skimr)
library(janitor)
```

## Exercises

### Exercise 1
```{r inspect-earthquakes}
skim(earthquakes)
```
The skim function serves as a read function in order to view the earthquake data.

### Exercise 2
```{r label-me1, eval=FALSE}
earthquakes_1 <- read_csv("data/earthquakes-1.csv",show_col_types = F)

earthquakes_2 <- read_tsv("data/earthquakes-2.txt",show_col_types = F)

earthquakes_3 <- read_xlsx("data/earthquakes-3.xlsx")
```

### Exercise 3

```{r inspect-earthquakes-1}
glimpse(earthquakes_1)
```
```{r inspect-earthquakes-2}
glimpse(earthquakes_2)
```
```{r inspect-earthquakes-3}
glimpse(earthquakes_3)
```
1. The first data set is missing the Richter and deaths variables. The second data set is missing the deaths and region/area variables. The third data set is missing the Richter and region/area variables.
2.The deaths variable in earthquakes_3 is a character string rather than a numerical string. 
3. The purpose of the coerce-earthquakes-3 code chunk is to coerce the deaths variable into the numerical data type.

### Exercise 4

```{r join-earthquakes}
earthquakes_1 %>% full_join(earthquakes_2, by=c("year","month","day")) %>% full_join(earthquakes_3, by=c("year","month","day")) %>% skim()

```


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
